From physical principles to ???

### 2016-03-03 2015CompleteDerivation/completeDerivation.tex
Incorporated Isaac feedback

% Status: Conceptual work done. Text ready for review. Incorporated Dave feedback

@@

Suppose we study the motion of a cannonball, its state under gravitational and inertial forces will be properly described by the position and momentum of the center of mass. While light and air molecules scatter off its surface randomly, its trajectory is not greatly affect as it is a massive rigid body. Suppose we study the motion of a small particle, small enough that the random scattering does influence the trajectory and it undergoes Brownian motion: its state will be a probability distribution for position and momentum of the center of mass. Gravitational and inertial forces have not changed, yet the set of states have. The issue is that the non-deterministic evolution must not change the set of states itself. That is: if we apply the non-deterministic evolution to any state, we still need to end up in one of the possible states. If the Brownian motion is strong enough, a simple position/momentum pair is not sufficient.

@@

Fourth, to be able to ascribe a property to a system we need to claim that, at least for a finite period of time, the system either held or did not hold such property. That is: there is a deterministic and reversible process for that finite period of time for such property.

>>>>

% Status: Conceptual work done. Text ready for review. Incorporated Dave and Isaac feedback

@@

Suppose we study the motion of a cannonball, its state under gravitational and inertial forces will be properly described by the position and momentum of the center of mass. While light and air molecules scatter off its surface randomly, its trajectory is not greatly affect as it is a massive rigid body. Suppose we study the motion of a small particle, small enough that the random scattering does influence the trajectory and it undergoes Brownian motion: its state will be a probability distribution for position and momentum of the center of mass. Gravitational and inertial forces have not changed, yet the set of states have. In other words: the set of states must also be closed under non-deterministic. If the Brownian motion is not negligible, we do not end in a well defined position/momentum pair, even if we start from one. %Reworded this for Isaac

@@

Fourth, to be able to ascribe a property to a system we need to claim that, at least for a finite interval of time, the system either held or did not hold such property. That is: there is a deterministic and reversible process for that finite period of time for such property.
